---
title: "BF design analysis for SP13 replication"
author: '[Guillermo Montero-Melis](https://www.mpi.nl/people/montero-melis-guillermo)'
date: '`r as.character(format(Sys.Date(), format="%d/%m/%Y"))`'
output:
  html_document:
    depth: 2
    number_sections: yes
    theme: default
    toc: yes
---


Introduction
============

This script carries out a number of Bayes factor design analyses (BFDA) based on
the framework laid out in Schönbrodt and Wagenmakers (2017, *Psychon Bull Rev*).
All BFDA apply to our intended replication of Shebani and Pulvermüller 
(2013, *Cortex*), henceforth SP13.

What differs between the BFDAs are the assumptions we make about a) effect size
and b) the type of test we will carry out. See details below.


Setup workspace
===============

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library("knitr")
library("tidyverse")  # ggplot2, dplyr, readr, purrr, etc
library("boot")       # for inv.logit()
library("BFDA")
```

Load posterior estimates from `brms` model fitted to original data (these come
from our reanalysis of the original data, see `reanalysis_original.Rmd`):

```{r}
# read and convert to vector
beta_post <- read_csv("sims_etc/beta_posterior.csv") %>%
  pull(1)
```



BFDA using effect size and analysis as in the original study
============================================

SP13 report an effect size of Cohen's $d = 1.25$ (p.226) for the critical
interaction effect obtained from a within-subjects ANOVA. Our first BFDA
follows this estimate, applying a paired t-test design, which is the closest
available test to the within-subjects ANOVA, and also the one that naturally
accepts Cohen's $d$ as an effect size estimate.

We run two versions of the simulation, once with the default (non-informative)
prior and once with an informed prior (Stefan et al., 2019, *Behav Res Meth*).
The latter uses a prior that places a stronger belief on there actually being
an effect. It is described as "an example for a typical informed prior for the
field of psychology" (Stefan et al., 2019, p. 1045). The values of the default
and informed priors are exactly those used in Stefan et al. (2019).


Default prior
------------

Run simulations:

```{r}
# # Run simulations and save to disk:
#
# # Under alternative hypothesis H1 with ES d = 1.25
# sim_H1_d_125_defPrior <- BFDA.sim(
#   expected.ES = 1.25,  # as reported in SP13
#   type = "t.paired",
#   prior=list("Cauchy",list(prior.location=0, prior.scale=sqrt(2)/2)),  # default non-informative
#   n.min=12, n.max=96, stepsize = 12, boundary=Inf,
#   alternative="greater",
#   B=2000, verbose=TRUE, cores=1)
# 
# # [1] "Simulation started at 2019-09-02 10:48:30"
# # [1] "Simulation finished at 2019-09-02 10:53:23"
# # Duration: Time difference of 4.876747 mins
# 
# # Save to disk:
# write_rds(sim_H1_d_125_defPrior, "sims_etc/sim_H1_d_125_defPrior.rds")
# 
# # Under null hypothesis H0
# sim_H0_d_125_defPrior <- BFDA.sim(
#   expected.ES = 0,  # under H0
#   type = "t.paired",
#   prior=list("Cauchy",list(prior.location=0, prior.scale=sqrt(2)/2)),  # default non-informative
#   n.min=12, n.max=96, stepsize = 12, boundary=Inf,
#   alternative="greater",
#   B=2000, verbose=TRUE, cores=1)
# 
# # [1] "Simulation started at 2019-09-02 10:54:52"
# # [1] "Simulation finished at 2019-09-02 11:04:19"
# # Duration: Time difference of 9.448281 mins
# 
# # Save to disk:
# write_rds(sim_H0_d_125_defPrior, "sims_etc/sim_H0_d_125_defPrior.rds")
```

Once run, load from disk:

```{r}
# Load from disk
sim_H1_d_125_defPrior <- read_rds("sims_etc/sim_H1_d_125_defPrior.rds")
sim_H1_d_125_defPrior

sim_H0_d_125_defPrior <- read_rds("sims_etc/sim_H0_d_125_defPrior.rds")
sim_H0_d_125_defPrior
```



Informed prior
--------------

Run simulations (only the `prior` argument changes):

```{r}
# Run simulations and save to disk:

# Under alternative hypothesis H1 with ES d = 1.25
sim_H1_d_125_infPrior <- BFDA.sim(
  expected.ES = 1.25,  # as reported in SP13
  type = "t.paired",
  prior=list("t", list(prior.location=0.35, prior.scale=0.102, prior.df=3)),  # informed prior following Stefan et al. (2019, p.1045)
  n.min=12, n.max=96, stepsize = 12, boundary=Inf,
  alternative="greater",
  B=2000, verbose=TRUE, cores=1)

# [1] "Simulation started at 2019-09-02 10:48:30"
# [1] "Simulation finished at 2019-09-02 10:53:23"
# Duration: Time difference of 4.876747 mins

# Save to disk:
write_rds(sim_H1_d_125_infPrior, "sims_etc/sim_H1_d_125_infPrior.rds")

# Under null hypothesis H0
sim_H0_d_125_infPrior <- BFDA.sim(
  expected.ES = 0,  # under H0
  type = "t.paired",
  prior=list("t", list(prior.location=0.35, prior.scale=0.102, prior.df=3)),  # informed prior following Stefan et al. (2019, p.1045)
  n.min=12, n.max=96, stepsize = 12, boundary=Inf,
  alternative="greater",
  B=2000, verbose=TRUE, cores=1)

# [1] "Simulation started at 2019-09-02 10:54:52"
# [1] "Simulation finished at 2019-09-02 11:04:19"
# Duration: Time difference of 9.448281 mins

# Save to disk:
write_rds(sim_H0_d_125_infPrior, "sims_etc/sim_H0_d_125_infPrior.rds")
```

Once run, load from disk:

```{r}
# Load from disk
sim_H1_d_125_infPrior <- read_rds("sims_etc/sim_H1_d_125_infPrior.rds")
sim_H1_d_125_infPrior

sim_H0_d_125_infPrior <- read_rds("sims_etc/sim_H0_d_125_infPrior.rds")
sim_H0_d_125_infPrior
```



BFDA with analysis as in the original study and effect size from our re-analysis
=======================================================================




BFDA based on our improved re-analysis (binomial GLMM) of the original data
=======================================================================


Effect size as estimated from the data
--------------------------------------



Effect size set to a small-to-medium effect
-------------------------------------------







Session info
============

```{r}
sessionInfo()
```

